---
format:
  gfm:
    default-image-extension: ""
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r}
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(width = 120)
```

# econio

<!-- badges: start -->
[![R-CMD-check](https://github.com/UchidaMizuki/econio/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/UchidaMizuki/econio/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/UchidaMizuki/econio/graph/badge.svg)](https://app.codecov.io/gh/UchidaMizuki/econio)
<!-- badges: end -->

econio provides a set of functions for input-output analysis.

## Installation

You can install the development version of econio from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("UchidaMizuki/econio")
```

## Example

```{r}
#| label: example
#| message: false
#| warning: false
library(econio)

library(econiodatajp)
library(ggplot2)
```

### Create an input-output table object

[econiodatajp](https://github.com/UchidaMizuki/econiodatajp) provides Japan's
input-output tables as ready-to-use `econ_io_table` objects, so you don't need
to build one from a tidy data frame yourself. Use `io_table_get()` to fetch a
specific table:

```{r}
#| label: create-input-output-table-object
iotable <- io_table_get(
  2020,
  region_type = "regional",
  area = "nation",
  sector_class = "large",
  language = "en"
)
iotable
```

### Calculate input coefficients and Leontief inverse matrix

```{r}
#| label: calculate-input-coef-and-leontief-inverse
io_input_coef(iotable)
io_leontief_inverse(iotable)
```

### Draw a skyline chart

```{r}
#| label: draw-skyline-chart
#| fig.width: 10
#| fig.height: 6
autoplot(iotable, type = "skyline")
```
