---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# econio

<!-- badges: start -->
[![R-CMD-check](https://github.com/UchidaMizuki/econio/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/UchidaMizuki/econio/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/UchidaMizuki/econio/graph/badge.svg)](https://app.codecov.io/gh/UchidaMizuki/econio)
<!-- badges: end -->

econio provides a set of functions for input-output analysis. 

## Installation

You can install the development version of econio from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("UchidaMizuki/econio")
```

## Example

```{r example, message=FALSE, warning=FALSE}
library(econio)

library(tidyverse)
library(iotables)
```

### Create an input-output table object

First, You need to prepare an input-output table in a tidy format. 
Then, you can create an input-output table object by using `io_table_regional()` function.

```{r create-input-output-table-object}
table_germany_1995 <- iotable_get(source = "germany_1995") |> 
  rename(input_sector_name = iotables_row) |>
  pivot_longer(!input_sector_name,
               names_to = "output_sector_name",
               values_to = "value") |>
  mutate(input_sector_type = case_match(input_sector_name,
                                        "total" ~ "industry",
                                        "imports" ~ "import",
                                        "net_tax_products" ~ "value_added"),
         output_sector_type = case_match(output_sector_name,
                                         "total" ~ "industry",
                                         "gross_capital_formation" ~ "final_demand",
                                         "exports" ~ "export")) |>
  relocate(input_sector_type, input_sector_name, output_sector_type, output_sector_name) |>
  fill(input_sector_type, output_sector_type,
       .direction = "up") |>
  drop_na(input_sector_type, output_sector_type) |>
  filter(!input_sector_name %in% c("total", "intermediate_consumption", "gva", "output"),
         !output_sector_name %in% c("total", "total_final_use"))
table_germany_1995

# You can suppress the message by setting `competitive_import = FALSE`
iotable_germany_1995 <- io_table_regional(table_germany_1995)
iotable_germany_1995
```

### Calculate input coefficients and Leontief inverse matrix

```{r calculate-input-coef-and-leontief-inverse}
io_input_coef(iotable_germany_1995)
io_leontief_inverse(iotable_germany_1995)
```

### Draw a skyline chart

```{r draw-skyline-chart}
iotable_germany_1995 |> 
  io_table_to_competitive_import() |> 
  autoplot(type = "skyline")
```
